### 2016-04-12 ch02-qlogms/excitation-design.tex
Fix some inconsistencies
Externalized lots of data files in CH02
Fix references in Ch02

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics~\citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing~\citep{GarciaLopez2014,DAmico2014} amongst others.

@@

  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).
  %TODO: mention crest factor? (here compensation/pink hurts)

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\omegaLinLog, +\infty}$, where
  \begin{equation}
    \omegaLinLog \isdef \frac{2\pi \Delta f}{\alpha - 1}
    \label{eq:excitation:linearLogTransitionFrequency}
  \end{equation}
  indicates the lowest frequency where the quasi-logarithmic grid can effectively reproduce the logarithmic spacing.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  %TODO: turn this into a guideline?
  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

>>>>

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances \citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy \citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics \citep{Munir2011}, mechatronics \citep{Steinbuch1998,Oomen2016}, vibration analysis~\citep{Karnopp1995,Voorhoeve2015SYSID} and acoustic testing \citep{GarciaLopez2014,DAmico2014} amongst others.

@@

  We can expect a very similar behavior from properly designed compensated quasi-log multisines and from the `pink' quasi-log multisine, since their amplitude spectra are almost identical.
  As such, it is advised to use `pink' quasi-log multisines as those can be constructed using more straightforward code (equation \eqref{eq:excitation:pink}) than the compensated quasi-log multisines (equations \eqref{eq:excitation:nfk}, \eqref{eq:excitation:nearestLines} , and \eqref{eq:excitation:compensationAk}).

@@

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\omegaLinLog, +\infty}$, where
  \begin{equation}
    \omegaLinLog \isdef \frac{2\pi \Delta f}{\alpha - 1}
    \label{eq:excitation:linearLogTransitionFrequency}
  \end{equation}
  indicates the lowest frequency where the quasi-logarithmic grid can effectively reproduce the logarithmic spacing.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \omegaLinLog =\frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  %TODO: turn this into a guideline?
  For more reliable results, however, it is advisable to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.
